Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-13 paper.tex
ADD links

\begin{abstract}
\citet{campbell2006efficient} propose a Bonferroni-type procedure for valid inference of predictive regressions with almost nonstationary regressors. In this study, the rationale behind their method is explained. Empirical findings are replicated and extended with out-of-sample data that emerged since the method's publication. Furthermore, the method's behavior is investigate via Monte Carlo simulation, highlighting practically relevant scenarios where it over-rejects the null hypothesis of no predictability. 
\end{abstract}

@@

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A common approach is to perform a t-test of $\beta$. \citet{elliott1994inference}, however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being greater than some deemed-acceptable nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in section $\ref{pretest}$.

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, \citet{campbell2006efficient} start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the demeaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and can thus not be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus the t-test ignores information about $\rho$.

@@

For the test-statistic to have a standard normal distribution under the null, \citet{campbell2006efficient} propose to recenter and rescale it, which results in 
\begin{equation}
\frac{\sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{2}\right)^{1 / 2}}>C.
\end{equation}
Revoking the previous assumption of $\alpha=\gamma=0$ and generalizing instead to any unknown  $\alpha$ and $\gamma$ by replacing $x_{t-1}$ by its demeaned value $x_{t-1}^{\mu}$, the test
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}}>C
\end{equation}
is UMP conditional on $\sum_{t=1}^{T} x_{t-1}^{\mu 2}$.
This Q-statistic, as \citet{campbell2006efficient} call it, has an intuitive interpretations when $\beta_{0} = 0$. It is the t-statistic of the $\beta^{\star}$ coefficient in the regression
 \begin{equation}
 \label{eqn:r_star}
r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)=\alpha^{\star}+\beta^{\star} x_{t-1}+v_{t}. 
\end{equation}
Regression ($\ref{eqn:r_star}$) can be interpreted as regressing the de-noised returns onto the regressor $x_{t-1}$, where the information contained in $\rho$ and the correlation of the shocks is exploited.
When $\beta_{u e}=0$, i.e., the correlation of the shocks is zero, the Q-statistic simplifies to the t-statistic which converges to a standard-normal distribution in this case. When $\beta_{u e}\neq0$, the t-statistic does not converge to a standard normal distribution. Instead, as shown by \citet{elliott1994inference}, under local-to-unity asymptotic theory it has the null distribution 
\begin{equation}
\label{lua_t}
t\left(\beta_{0}\right) \Rightarrow \delta \frac{\tau_{c}}{\kappa_{c}}+\left(1-\delta^{2}\right)^{1 / 2} Z,
\end{equation}
where $\left(W_{u}(s), W_{e}(s)\right)^{\prime}$ is a two-dimensional Wiener process with correlation $\delta$, $J_{c}(s)$ is defined by $\mathrm{d} J_{c}(s)=c J_{c}(s) \mathrm{d} s+\mathrm{d} W_{e}(s)$ with $J_{c}(0)=0$, $Z$ is a standard normal random variable independent of $\left(W_{e}(s), J_{c}(s)\right)$, $\kappa_{c}=\left(\int J_{c}^{\mu}(s)^{2} \mathrm{d} s\right)^{1 / 2}$, and $\tau_{c}=\int J_{c}^{\mu}(s) \mathrm{d} W_{e}(s)$.

@@

\citet{campbell2006efficient} use these facts as bases for a pretest. This test supposes that an actual size $\alpha^{\star}  \geq \alpha$ may be acceptable if its not much greater than the nominal size $\alpha$. It then tests whether $\alpha^{\star}$ is greater than a prespecified acceptable size. It would be tempting to use a unit root test and infer no size distortion if its null of nonstationarity can be rejected. \citet{elliott1994inference} show, however, that this does not guarantee valid inference via the t-statistic. Instead, \citet{campbell2006efficient} use a unit root test statistic to construct a confidence interval for $c$ by inverting its alternative distribution in the spirit of \citet{stock1991confidence}. $\delta$, on the other hand, can be consistently estimated from the residuals of regressions ($\ref{eqn:1}$, $\ref{eqn:2}$). The size of the t-statistic forms a two-dimensional surface in the $c$-$\delta$-parameter space. If the confidence interval for $c$ lies strictly outside the region where the size is above the acceptable threshold for $\hat{\delta}$, the null of unacceptable size distortion can be rejected. This test is implemented with tables provided by \citet{campbell2006efficient}, who use the DF-GLS test statistic proposed by \citet{elliott1996efficient} to construct the confidence interval for $c$. The application accompanying uses the closest tabulated values to the estimated values without interpolating.

@@

When the pretest cannot reject the null of unacceptable size distortion inference cannot be based the t-test without adjustment. While the Q-test is UMP when $\rho$ and $\delta$ are known, in practice this is not the case. Furthermore, $\rho$ cannot be estimated consistently since its OLS estimator converges at rate $T$. Instead, analogously to the description in the previous section, \citet{campbell2006efficient} construct a $100\left(1-\alpha_{1}\right) \%$ confidence interval, $C_{\rho}\left(\alpha_{1}\right)$ for $\rho$ from a unit root test statistic. They then construct $C_{\beta | \rho}\left(\alpha_{2}\right)$, a $100\left(1-\alpha_{2}\right) \%$ conditional on $\rho$ confidence interval for $\beta$. To marginalize $\rho$ and thus getting an unconditional confidence interval for $\beta$ they take the union over $\rho \in C_{\rho}\left(\alpha_{1}\right)$

@@

with $C_{\rho}\left(\alpha_{1}\right)= \left[\underline{\rho}\left(\underline{\alpha}_{1}\right), \overline{\rho}\left(\overline{\alpha}_{1}\right)\right]$ being the confidence interval for $\rho$, $\underline{\alpha}_{1}=\operatorname{Pr}\left(\rho<\underline{\rho}\left(\underline{\alpha}_{1}\right)\right)$, $\overline{\alpha}_{1}=\operatorname{Pr}\left(\rho>\overline{\rho}\left(\overline{\alpha}_{1}\right)\right)$, and $\alpha_{1}=\underline{\alpha}_{1}+\overline{\alpha}_{1}$. We also know that the Q-statistic is normally distributed. Let $z_{\alpha_{2} / 2}$ denote the $1-\alpha_{2} / 2$ quantile of the standard normal distribution. Then the lower bound is given by

@@

The feasible Q-test, generalized to less restrictive assumptions, is implemented in the R programming language of \citet{R} following the steps proposed by \citet{campbell2005implementing}. Suppose the regressor follows an $AR(p)$ process. Further, the innovations are not necessarily normally distributed but are a martingale difference sequence, i.e., 
\begin{equation}
\mathrm{E}\left[w_{t} |\mathscr{F}_{t-1}\right]=0
\end{equation}
where $\mathscr{F}_{t}=\left\{w_{s} | s \leq t\right\}$ denotes the filtration generated by $w_{t}=\left(u_{t}, e_{t}\right)^{\prime}$.
Its fourth moments are assumed to be finite and the unconditional variance is fixed, i.e.,
\begin{equation}
\label{eqn:covarst}
\begin{array}{l}{\mathrm{E}\left[w_{t} w_{t}^{\prime}\right]=\Sigma} \\ {\sup _{t} \mathrm{E}\left[u_{t}^{4}\right]<\infty, \sup _{t} \mathrm{E}\left[t_{t}^{4}\right]<\infty, \text { and } \mathrm{E}\left[x_{0}^{2}\right]<\infty.}\end{array}
\end{equation}
The dynamics of $x_{t}$ are written as
\begin{equation}
\label{eqn:22}
x_{t}=\gamma+\rho x_{t-1}+v_{t},
\end{equation}
where $\rho$ is the largest autoregressive root and $b(L) v_{t}=e_{t}$ with $b(L)=\sum_{i=0}^{p-1} b_{i} L^{i}$, $b_{0}=1$, and $b(1) \neq 0$. In this generalized case, the Q-statistic is not asymptotically standard normal distributed under the null. This is corrected by modifying it to
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\sigma_{u e} /\left(\sigma_{e} \omega\right)\left(x_{t}-\rho x_{t-1}\right)\right]+\frac{T}{2} \sigma_{u e} /\left(\sigma_{e} \omega\right)\left(\omega^{2}-\sigma_{v}^{2}\right)}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}},
\end{equation}
where $\omega=\sigma_{e} / b(1)$.

@@

\section{Monte Carlo simulation}
This section, next to the out-of-sample results in section $\ref{Empirical Results}$, accommodates one of the main contributions of this study. First, Monte Carlo evidence of \citet{campbell2006efficient} is replicated providing reassurance that both parties implemented the method correctly. Next, the Bonferroni Q-test is tested by violating key assumptions about the regressor's persistence. Furthermore, innovations are modeled by increasingly realistic distributions, for which justification in the form of real-world parameter estimates is given.
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of \citet{campbell2006efficient} with the same input parameters. For each parameter combination, 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by \citet{phillips2014confidence}, the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrated as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of \citet{campbell2005implementing}. Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of \citet{engle1995multivariate}. It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Parameter estimates of the univariate GARCH model based on monthly returns from 1926 to 2003 are displayed in Table~\vref{tab:garch_est}. Since $\hat{\alpha}+\hat{\beta}=0.983$ is close to 1, at which point the covariance stationarity condition is violated, concern of conditional heteroskedasticity of real returns leading to invalid inference using the feasible Q-test is justified.

@@

Table~\vref{tab:cy_sp} replicates the key results of Tables 4 and 5 of \citet{campbell2006efficient}. The Bonferroni Q-test is implemented as described in section $\ref{implementation}$. The regressors under consideration are the dividend-to-price ratio [ldp] and the earnings-to-price ratio [lep] where earnings, following \citet{shiller2000irrational}, are averaged over a moving 10-year period. Three different sampling frequencies, annual, quarterly, and monthly, are considered. Following \citet{campbell2006efficient}, the confidence interval for $\beta$ is scaled by $\widehat{\sigma}_{e} / \widehat{\sigma}_{u}$ such that interpretation is made easier as the coefficient in equation $\ref{eqn:1}$ with unit variance innovations. Right-tailed tests with null hypothesis $H_0: \beta=0$ against alternative $H_1: \beta>0$ are considered where the null is rejected at 5\% significance level if the lower bound of $\beta$'s 90\% confidence interval is greater than zero. Apart from rounding errors, the results are nearly the same except for the following discrepancies. First, the DF-GLS statistic for $p>1$ is higher than reported by \citet{campbell2006efficient}.  As previously mentioned, the DF-GLS implementation of section $\ref{implementation}$ was verified with a different open-source implementation. Second, based on the BIC, a lower $p$ of 1 was selected for monthly ldp. Investigations showed that the difference in BIC when $p=1$ compared with $p=2$ is very small. Thus the different selection is likely due to rounding errors. 

@@

\item Data is taken from Motohiro Yogo's website at https://drive.google.com/file/d/0BzR-ojpYuaFMcnZteHFyWUVIUFU/view. The regressors are the 10-year moving average earnings to current price ratio [lep] and the dividend to price ratio [ldp] in logs. Observations are recorded on a monthly [CRSP M], quarterly [CRSP Q], and annual basis [CRSP A] for CRSP (1926– 2002). For S\&P (1880– 2002) data is only available on an annual basis [SP A]. Stock returns are the SP 500 value weighted index log-returns from 1880 to 2003 minus the risk free rate and the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate. $p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.

>>>>

\begin{abstract}
\citet{campbell2006efficient} propose a Bonferroni-type procedure for valid inference of predictive regressions with almost nonstationary regressors. In this paper, the rationale behind their method is explained. Empirical findings are replicated and extended with out-of-sample data that emerged since the method's publication. Furthermore, the method's behavior is investigate via Monte Carlo simulation, highlighting practically relevant scenarios where it over-rejects the null hypothesis of no predictability. 
\end{abstract}

@@

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A common approach is to perform a t-test of $\beta$. \citet{elliott1994inference}, however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being unacceptably larger than nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in section $\ref{pretest}$.

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, \citet{campbell2006efficient} start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the demeaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and can thus not be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus, the t-test ignores information about $\rho$.

@@

For the test-statistic to have a standard normal distribution under the null, \citet{campbell2006efficient} propose to recenter and rescale it, which results in 
\begin{equation}
\frac{\sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{2}\right)^{1 / 2}}>C.
\end{equation}
Revoking the previous assumption of $\alpha=\gamma=0$ and generalizing instead to any unknown  $\alpha$ and $\gamma$ by replacing $x_{t-1}$ by its demeaned value $x_{t-1}^{\mu}$, the test
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}}>C
\end{equation}
is UMP conditional on $\sum_{t=1}^{T} x_{t-1}^{\mu 2}$.
This Q-statistic, as \citet{campbell2006efficient} call it, has an intuitive interpretations when $\beta_{0} = 0$. It is the t-statistic of the $\beta^{\star}$ coefficient in the regression
 \begin{equation}
 \label{eqn:r_star}
r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)=\alpha^{\star}+\beta^{\star} x_{t-1}+v_{t}. 
\end{equation}
Regression ($\ref{eqn:r_star}$) can be interpreted as regressing the denoised returns onto the regressor $x_{t-1}$, where the information contained in $\rho$ and the correlation of the shocks is exploited.
When $\beta_{u e}=0$, i.e., the correlation of the shocks is zero, the Q-statistic simplifies to the t-statistic which converges to a standard-normal distribution in this case. When $\beta_{u e}\neq0$, the t-statistic does not converge to a standard normal distribution. Instead, as shown by \citet{elliott1994inference}, under local-to-unity asymptotic theory it has the null distribution 
\begin{equation}
\label{lua_t}
t\left(\beta_{0}\right) \Rightarrow \delta \frac{\tau_{c}}{\kappa_{c}}+\left(1-\delta^{2}\right)^{1 / 2} Z,
\end{equation}
where $\left(W_{u}(s), W_{e}(s)\right)^{\prime}$ is a two-dimensional Wiener process with correlation $\delta$, $J_{c}(s)$ is defined by $\mathrm{d} J_{c}(s)=c J_{c}(s) \mathrm{d} s+\mathrm{d} W_{e}(s)$ with $J_{c}(0)=0$, $Z$ is a standard normal random variable independent of $\left(W_{e}(s), J_{c}(s)\right)$, $\kappa_{c}=\left(\int J_{c}^{\mu}(s)^{2} \mathrm{d} s\right)^{1 / 2}$, and $\tau_{c}=\int J_{c}^{\mu}(s) \mathrm{d} W_{e}(s)$.

@@

\citet{campbell2006efficient} use these facts as bases for a pretest. This test supposes that an actual size $\alpha^{\star}  \geq \alpha$ may be acceptable if its not much greater than the nominal size $\alpha$. It then tests whether $\alpha^{\star}$ is greater than a prespecified acceptable size. It would be tempting to use a unit root test and infer no size distortion if its null of nonstationarity can be rejected. \citet{elliott1994inference} show, however, that this does not guarantee valid inference via the t-statistic. Instead, \citet{campbell2006efficient} use a unit root test statistic to construct a confidence interval for $c$ by inverting its alternative distribution in the spirit of \citet{stock1991confidence}. $\delta$, on the other hand, can be consistently estimated from the residuals of regressions ($\ref{eqn:1}$, $\ref{eqn:2}$). The size of the t-statistic forms a two-dimensional surface in the $c$-$\delta$-parameter space. If the confidence interval for $c$ lies strictly outside the region where the size is above the acceptable threshold given $\hat{\delta}$, the null of unacceptable size distortion can be rejected. This test is implemented with tables provided by \citet{campbell2006efficient}, who use the DF-GLS test statistic proposed by \citet{elliott1996efficient} to construct the confidence interval for $c$. The application accompanying this paper uses the closest tabulated values to the estimated values without interpolating.

@@

When the pretest cannot reject the null of unacceptable size distortion, inference cannot be based on the t-test without adjustment. While the Q-test is UMP when $\rho$ and $\delta$ are known, in practice this is not the case. Furthermore, $\rho$ cannot be estimated consistently since its OLS estimator converges at rate $T$. Instead, analogously to the description in the previous section, \citet{campbell2006efficient} construct a $100\left(1-\alpha_{1}\right) \%$ confidence interval, $C_{\rho}\left(\alpha_{1}\right)$ for $\rho$ from a unit root test statistic. They then construct $C_{\beta | \rho}\left(\alpha_{2}\right)$, a $100\left(1-\alpha_{2}\right) \%$ conditional-on-$\rho$ confidence interval for $\beta$. To marginalize $\rho$ and thus getting an unconditional confidence interval for $\beta$ they take the union over $\rho \in C_{\rho}\left(\alpha_{1}\right)$

@@

with $C_{\rho}\left(\alpha_{1}\right)= \left[\underline{\rho}\left(\underline{\alpha}_{1}\right), \overline{\rho}\left(\overline{\alpha}_{1}\right)\right]$ being the confidence interval for $\rho$, $\underline{\alpha}_{1}=\operatorname{Pr}\left(\rho<\underline{\rho}\left(\underline{\alpha}_{1}\right)\right)$, $\overline{\alpha}_{1}=\operatorname{Pr}\left(\rho>\overline{\rho}\left(\overline{\alpha}_{1}\right)\right)$, and $\alpha_{1}=\underline{\alpha}_{1}+\overline{\alpha}_{1}$. The Q-statistic is also known to be normally distributed. Let $z_{\alpha_{2} / 2}$ denote the $1-\alpha_{2} / 2$ quantile of the standard normal distribution. Then the lower bound is given by

@@

The feasible Q-test, generalized to less restrictive assumptions, is implemented in the R programming language of the \citet{R} following the steps proposed by \citet{campbell2005implementing}\footnote{The source code is available at https://github.com/jpwoeltjen/PersistentRegressors/tree/master/pr.}. Suppose the regressor follows an $AR(p)$ process. Further, the innovations are not necessarily normally distributed but are a martingale difference sequence, i.e., 
\begin{equation}
\mathrm{E}\left[w_{t} |\mathscr{F}_{t-1}\right]=0,
\end{equation}
where $\mathscr{F}_{t}=\left\{w_{s} | s \leq t\right\}$ denotes the filtration generated by $w_{t}=\left(u_{t}, e_{t}\right)^{\prime}$.
Its fourth moments are assumed to be finite and the unconditional variance is fixed, i.e.,
\begin{equation}
\label{eqn:covarst}
\begin{array}{l}{\mathrm{E}\left[w_{t} w_{t}^{\prime}\right]=\Sigma} \\ {\sup _{t} \mathrm{E}\left[u_{t}^{4}\right]<\infty, \sup _{t} \mathrm{E}\left[t_{t}^{4}\right]<\infty, \text { and } \mathrm{E}\left[x_{0}^{2}\right]<\infty.}\end{array}
\end{equation}
The dynamics of $x_{t}$ are written as
\begin{equation}
\label{eqn:22}
x_{t}=\gamma+\rho x_{t-1}+v_{t},
\end{equation}
where $\rho$ is the largest autoregressive root and $b(L) v_{t}=e_{t}$ with $b(L)=\sum_{i=0}^{p-1} b_{i} L^{i}$, $b_{0}=1$, and $b(1) \neq 0$. In this generalized case, the Q-statistic is not asymptotically standard normal distributed under the null. This is corrected by modifying it to
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\sigma_{u e} /\left(\sigma_{e} \omega\right)\left(x_{t}-\rho x_{t-1}\right)\right]+\frac{T}{2} \sigma_{u e} /\left(\sigma_{e} \omega\right)\left(\omega^{2}-\sigma_{v}^{2}\right)}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}},
\end{equation}
where $\omega=\sigma_{e} / b(1)$.

@@

\section{Monte Carlo simulation}
This section, next to the out-of-sample results in section $\ref{Empirical Results}$, accommodates one of the main contributions of this paper.\footnote{All code generating the Monte Carlo results is available at https://github.com/jpwoeltjen/\\PersistentRegressors/tree/master/MonteCarlo.} First, Monte Carlo evidence of \citet{campbell2006efficient} is replicated providing reassurance that both parties implemented the method correctly. Next, the Bonferroni Q-test is tested by violating key assumptions about the regressor's persistence. Furthermore, innovations are modeled by increasingly realistic distributions, for which justification in the form of real-world parameter estimates is given.
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of \citet{campbell2006efficient} with the same input parameters. For each parameter combination, 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by \citet{phillips2014confidence}, the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrated as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of \citet{campbell2005implementing}. Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood, the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of \citet{engle1995multivariate}. It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Parameter estimates of the univariate GARCH model based on monthly returns from 1926 to 2003 are displayed in Table~\vref{tab:garch_est}. Since $\hat{\alpha}+\hat{\beta}=0.983$ is close to unity, at which point the covariance stationarity condition is violated, concern of conditional heteroskedasticity of real returns leading to invalid inference using the feasible Q-test is justified.

@@

Table~\vref{tab:cy_sp} replicates the key results of Tables 4 and 5 of \citet{campbell2006efficient}. The Bonferroni Q-test is implemented as described in section $\ref{implementation}$. The regressors under consideration are the dividend-to-price ratio [ldp] and the earnings-to-price ratio [lep], where earnings, following \citet{shiller2000irrational}, are averaged over a moving 10-year period. Three different sampling frequencies, annual, quarterly, and monthly, are considered. Following \citet{campbell2006efficient}, the confidence interval for $\beta$ is scaled by $\widehat{\sigma}_{e} / \widehat{\sigma}_{u}$ such that interpretation is made easier as the coefficient in equation ($\ref{eqn:1}$) with unit variance innovations. Right-tailed tests with null hypothesis $H_0: \beta=0$ against alternative $H_1: \beta>0$ are considered, where the null is rejected at 5\% significance level if the lower bound of $\beta$'s 90\% confidence interval is greater than zero. Apart from rounding errors, the results are nearly the same except for the following discrepancies. First, the DF-GLS statistic for $p>1$ is higher than reported by \citet{campbell2006efficient}.  As previously mentioned, the DF-GLS implementation of section $\ref{implementation}$ was verified with a different open-source implementation. Second, based on the BIC, a lower $p$ of 1 was selected for monthly ldp. Investigations showed that the difference in BIC when $p=1$ compared with $p=2$ is very small. Thus the different selection is likely due to rounding errors. 

@@

\item Data is taken from Motohiro Yogo's website at https://drive.google.com/file/d/0BzR-ojpYuaFMcnZteHFyWUVIUFU/view. The code generating this table is available at https://github.com/jpwoeltjen/PersistentRegressors. The regressors are the 10-year moving average earnings to current price ratio [lep] and the dividend to price ratio [ldp] in logs. Observations are recorded on a monthly [CRSP M], quarterly [CRSP Q], and annual basis [CRSP A] for CRSP (1926– 2002). For S\&P (1880– 2002) data is only available on an annual basis [SP A]. Stock returns are the SP 500 value weighted index log-returns from 1880 to 2003 minus the risk free rate and the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate. $p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
